Methods paper for erosion

### 2017-11-20 docs/methods/erosion_methods.tex
Added some figures to the paper
Added note

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& M = - 2 \pi \mean{\thalpha \Vn} \\
\label{eq:N}
& N = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
\label{eq:elfun}
& \elfun = \frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
\end{equation}
Note that the $\elfun$ depends only on $L(t)$, and so the highest order
derivative in Eq.~\eqref{eqn:thetaevo1} is {\em linear} in the variable $\alpha$. This is the key to the {\thL} method, and allows us to use very stable, implicit methods for the stiff term. We will evolve $\theta$ in spectral space, and so introduce the transforms
\begin{align}
& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{ i k \alpha} \\
& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{ i k \alpha}
\end{align}
Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
\begin{equation}
\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{N}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\label{eq:mu}
\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
\end{equation}
Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = M \\
\label{eqn:thetaevo2}
& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{N}_k
\end{align}
We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with a combination of an explicit, second-order Runge-Kutta method (RK2) and trapezoid rule to compute the integrating factor, $\mu_k$. There is not a unique second-order Runge-Kutta method, and we choose the {\em midpoint} version to maximize the smoothing effect of the curvature term.

@@

>>>>

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& M = - 2 \pi \mean{\thalpha \Vn} \\
\label{eq:N}
& N = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
\label{eq:elfun}
& \elfun = \frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
\end{equation}
\todo[inline]{Change $N$ to something else $\mathcal{N}$}
Note that the $\elfun$ depends only on $L(t)$, and so the highest order
derivative in Eq.~\eqref{eqn:thetaevo1} is {\em linear} in the variable $\alpha$. This is the key to the {\thL} method, and allows us to use very stable, implicit methods for the stiff term. We will evolve $\theta$ in spectral space, and so introduce the transforms
\begin{align}
& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{ i k \alpha} \\
& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{ i k \alpha}
\end{align}
Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
\begin{equation}
\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{N}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\label{eq:mu}
\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
\end{equation}
Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = M \\
\label{eqn:thetaevo2}
& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{N}_k
\end{align}
We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with a combination of an explicit, second-order Runge-Kutta method (RK2) and trapezoid rule to compute the integrating factor, $\mu_k$. There is not a unique second-order Runge-Kutta method, and we choose the {\em midpoint} version to maximize the smoothing effect of the curvature term.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/fig3.pdf}
\caption{Shrinking body and area.}
\label{fig1}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
\caption{Final shape.}
\label{fig2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
